SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2018-08-11 scipy-1.0/paper.tex

>>>>

\texttt{scipy.sparse} offers seven sparse matrix data structures,
also known as sparse formats. The most important ones are the row- 
and column-compressed formats (CSR and CSC, respectively). 
These offer fast major-axis indexing and fast matrix-vector multiplication,
and are used heavily in scikit-learn.

Over the last three years our sparse matrix handling internals have
been rewritten and performance has been improved. Iterating over 
and slicing of CSC and CSR matrices is now faster by up to 35\%,
and the CSR to COO matrix format conversion is now several times faster.
Importantly, SuperLU\cite{superlu_ug99} was updated to version 5.2.1, enhancing
the low-level implementations leveraged by a subset of our \texttt{sparse}
offerings.

From a new features standpoint, \texttt{scipy.sparse} matrices and linear
operators now support the Python matrix multiplication (@) operator when
available. We've added \texttt{scipy.sparse.norm} and \texttt{scipy.sparse.random} 
for computing sparse matrix norms and drawing random variates from arbitrary 
distributions, respectively. Also, we've made a concerted effort to bring the
\texttt{scipy.sparse} API into line with the equivalent NumPy API where possible.
